\paperheader
    {Electromagnetic Phenomena in a System Moving with Any Velocity Less Than That of Light}
    {H. A. Lorentz}
    {...}


\section{Introduction}
Assume that the laws of physics take the same form in every inertial frame and that the speed of light in vacuum is constant. Then space and time can no longer be treated as isolated absolute quantities; instead, they must be related through a unified transformation law. This paper section demonstrates a clean collection layout with equations, tables, figures, and footnotes.\footnote{Footnotes are best used for supplementary remarks, publication details, or historical notes rather than for the main argument itself.}

\section{Formula Example}
The Lorentz transformation may be written as
\begin{equation}
\label{eq:lorentz}
\begin{aligned}
x' &= \gamma(x - vt),\\
t' &= \gamma\left(t - \frac{vx}{c^2}\right),\\
y' &= y,\qquad z' = z,
\end{aligned}
\end{equation}
where
\begin{equation}
\gamma = \frac{1}{\sqrt{1-\dfrac{v^2}{c^2}}}.
\end{equation}
From \eqref{eq:lorentz} one obtains the Minkowski interval
\begin{equation}
s^2 = c^2 t^2 - x^2 - y^2 - z^2,
\end{equation}
which remains invariant under the transformation.

\begin{theorem}
If two inertial frames are related by a Lorentz transformation, then the spacetime interval $s^2$ is invariant.
\end{theorem}

\begin{proof}
Substitute $x', y', z', t'$ into the expression $c^2 t'^2 - x'^2 - y'^2 - z'^2$. After expansion and simplification, the mixed terms cancel and the result reduces to $c^2 t^2 - x^2 - y^2 - z^2$.
\end{proof}

\section{Table Example}
The table below lists the Lorentz factor for several representative velocities.

\begin{table}[htbp]
\centering
\caption{Lorentz factor at selected velocities}
\begin{tabular}{>{\centering\arraybackslash}p{3cm} >{\centering\arraybackslash}p{4cm} >{\centering\arraybackslash}p{4cm}}
\hline
Velocity $v/c$ & Expression for $\gamma$ & Approximate value \\
\hline
0.20 & $\dfrac{1}{\sqrt{1-0.20^2}}$ & 1.021 \\
0.50 & $\dfrac{1}{\sqrt{1-0.50^2}}$ & 1.155 \\
0.80 & $\dfrac{1}{\sqrt{1-0.80^2}}$ & 1.667 \\
0.95 & $\dfrac{1}{\sqrt{1-0.95^2}}$ & 3.203 \\
\hline
\end{tabular}
\end{table}

\section{Figure Example}
When external image assets are unnecessary, figures can be generated directly with \texttt{TikZ} and \texttt{PGFPlots}.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
  width=0.8\textwidth,
  height=6.5cm,
  xlabel={$v/c$},
  ylabel={$\gamma$},
  ymin=1,
  ymax=3.6,
  xmin=0,
  xmax=0.98,
  grid=major,
  thick,
  samples=200
]
\addplot[color=black,domain=0:0.95]{1/sqrt(1-x^2)};
\end{axis}
\end{tikzpicture}
\caption{The growth of the Lorentz factor as velocity increases}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[scale=1]
  \draw[->,thick] (-0.2,0) -- (5.2,0) node[right] {$x$};
  \draw[->,thick] (0,-0.2) -- (0,3.2) node[above] {$ct$};
  \draw[very thick,color=black] (0,0) -- (4.4,2.8) node[right] {$x'=0$};
  \draw[very thick,dashed,color=black] (0,0) -- (2.8,2.8) node[above] {$x=0$};
  \draw[dotted,color=black] (1.8,0) -- (1.8,1.15);
  \draw[dotted,color=black] (0,1.15) -- (1.8,1.15);
\end{tikzpicture}
\caption{A simplified spacetime sketch for two inertial frames}
\end{figure}

\section{Layout Remarks}
Every paper in the collection can preserve the same opening structure while allowing the body to expand freely according to the research topic. Longer derivations may continue with environments such as \texttt{align}, \texttt{gather}, or \texttt{split}; multipage tables may be handled with \texttt{longtable}.
